\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.45in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADER----------
\begin{center}
  {\Huge \scshape Mohammed Wasim Khan} \\ \vspace{1pt}
  Visakhapatnam, Andhra Pradesh, India \\ \vspace{1pt}
  \small +91-9640011405 ~
  \href{mailto:wasim143mr@gmail.com}{wasim143mr@gmail.com} ~
  \href{https://linkedin.com/in/mohammed-wasim-khan-757595245}{LinkedIn} ~
  \href{https://github.com/wasim-builds}{GitHub}
  \vspace{-8pt}
\end{center}

%----------PROFESSIONAL SUMMARY----------
\section{Professional Summary}
Full Stack Developer and AI/ML Engineer with expertise in building scalable web applications and intelligent data systems. Proficient in the MERN stack (MongoDB, Express.js, React, Node.js), Python, and Machine Learning frameworks including TensorFlow and Scikit-learn. Experienced in REST API design, database optimization, NLP pipelines, and RAG architectures. Currently working as a Software Development Instructor at NxtWave, with prior internship experience at Vizag Steel Plant. Passionate about building real-world solutions that combine strong engineering with data-driven intelligence.

%----------TECHNICAL SKILLS----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, JavaScript (ES6+), TypeScript, Java, C++, SQL, Bash, HTML5, CSS3} \\
    \textbf{Frontend}{: React, Angular, Vite, Redux, Tailwind CSS, Responsive Design} \\
    \textbf{Backend}{: Node.js, Express.js, Flask, FastAPI, RESTful APIs, JWT Authentication} \\
    \textbf{AI \& ML}{: TensorFlow, Scikit-learn, NLP, NLTK, Pandas, NumPy, RAG Architecture, Azure OpenAI, Deep Learning} \\
    \textbf{Databases}{: MongoDB, PostgreSQL, MySQL, SQLite, Query Optimization, Indexing} \\
    \textbf{Tools \& DevOps}{: Git, Docker, AWS, Linux, CI/CD, Postman, Jupyter Notebooks} \\
    \textbf{Core CS}{: Data Structures \& Algorithms, System Design, OOP, DBMS, Agile Methodologies}
  }}
\end{itemize}
\vspace{-16pt}

%----------EDUCATION----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{VIT-AP University, Amaravathi}{Nov 2021 -- Present}
{Integrated M-Tech in Software Engineering (Computer Science)}{CGPA: 8.33/10}
\resumeSubheading
{Narayana Junior College, Vizag}{May 2018 -- July 2020}
{Intermediate (MPC)}{CGPA: 8.88/10}
\resumeSubHeadingListEnd

%----------WORK EXPERIENCE----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Development Instructor Intern}{Apr 2026 -- Present}
{NxtWave Disruptive Technologies}{Hyderabad, IN (Hybrid)}
\resumeItemListStart
\resumeItem{Delivering frontend web development instruction covering React, JavaScript, and modern web technologies to students, translating complex concepts into structured, project-based learning paths.}
\resumeItem{Reviewing and debugging student projects daily, reinforcing best practices in component architecture, REST API integration, and database-driven application design.}
\resumeItem{Strengthened technical communication and documentation skills by explaining code architecture, UI/UX patterns, and debugging workflows to learners at varying skill levels.}
\resumeItemListEnd

\resumeSubheading
{Software \& Data Engineering Intern}{Jul 2024}
{Rashtriya Ispat Nigam Limited (Vizag Steel Plant)}{Visakhapatnam, IN}
\resumeItemListStart
\resumeItem{Built a full-stack healthcare management system using React and Node.js, handling 5,000+ daily transactions with robust data integrity and a 20\% reduction in patient wait times.}
\resumeItem{Designed automated ETL workflows eliminating 30\% of manual data entry errors across manufacturing operations, improving downstream data quality.}
\resumeItem{Optimized PostgreSQL and MySQL queries through execution plan analysis and indexing, reducing average response time from 850ms to 240ms — a 72\% improvement.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}

%----------PROJECTS----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{AI Interview Preparation Bot} $|$ \emph{React, Node.js, Azure OpenAI, RAG, MongoDB}}{Jan 2026}
\resumeItemListStart
\resumeItem{Architected a full-stack AI coaching platform using RAG architecture and Azure OpenAI to parse PDF resumes and deliver personalized, context-aware technical Q\&A, reducing preparation time by 40\%.}
\resumeItem{Designed RESTful APIs managing PDF ingestion, vector-based retrieval pipelines, and dynamic response delivery across a React frontend and Node.js/Express backend.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{CodeToCareer - Placement Platform} $|$ \emph{React, Node.js, Express.js, MongoDB, JWT}}{Dec 2025}
\resumeItemListStart
\resumeItem{Developed a comprehensive full-stack MERN platform with course management, real-time discussion forums, and role-based dashboards serving 200+ active users.}
\resumeItem{Built scalable RESTful APIs with JWT authentication achieving sub-150ms response times for 95\% of endpoints through performance profiling and query optimization.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Spam Email Detection System} $|$ \emph{Python, Scikit-learn, NLP, NLTK, TF-IDF}}{Mar 2025}
\resumeItemListStart
\resumeItem{Engineered an NLP classification pipeline processing 15,000+ samples using tokenization, stemming, and TF-IDF vectorization; benchmarked Naive Bayes, SVM, and Random Forest models.}
\resumeItem{Achieved 96\% precision and 0.95 F1-score through hyperparameter tuning, minimizing false positives critical for production-grade classification systems.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Smart Attendance System} $|$ \emph{Python, OpenCV, CNN, Deep Learning, MySQL}}{Aug 2024}
\resumeItemListStart
\resumeItem{Built a real-time facial recognition attendance system using CNN embeddings, achieving 98\% detection accuracy across 500+ student profiles.}
\resumeItem{Automated attendance logging via MySQL and SQLite handling 300+ daily scans, reducing manual processing time by 90\%.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Text-Based Emotion Classifier} $|$ \emph{Python, NLP, SVM, ANN, N-grams}}{Jun 2024}
\resumeItemListStart
\resumeItem{Implemented multilingual text classification using Naive Bayes, SVM, and ANN on Indian language datasets; engineered N-gram models to handle complex linguistic patterns and improve retrieval accuracy.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}

%----------CERTIFICATIONS----------
\section{Certifications \& Achievements}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Gemini Certified University Student} $|$ \emph{Google}}{Dec 2025}
\resumeProjectHeading
{\textbf{Object Oriented Programming - Basics to Advanced} $|$ \emph{Udemy}}{Nov 2023}
\resumeProjectHeading
{\textbf{University Chess Player} $|$ \emph{Strategic thinking and analytical problem solving}}{}
\resumeSubHeadingListEnd

\end{document}
