\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.45in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \textbf{\small #2}\\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADER----------
\begin{center}
  {\Huge \scshape Mohammed Wasim Khan} \\ \vspace{1pt}
  Visakhapatnam, Andhra Pradesh, India \\ \vspace{1pt}
  \small +91-9640011405 ~
  \href{mailto:wasim143mr@gmail.com}{wasim143mr@gmail.com} ~
  \href{https://linkedin.com/in/mohammed-wasim-khan-757595245}{LinkedIn} ~
  \href{https://github.com/wasim-builds}{GitHub}
  \vspace{-8pt}
\end{center}

%----------PROFESSIONAL SUMMARY----------
\section{Professional Summary}
Web Developer with solid expertise in building responsive, performant, and user-friendly web applications across the full stack. Proficient in React, JavaScript (ES6+), TypeScript, Node.js, and modern CSS frameworks including Tailwind CSS. Experienced in delivering cross-browser compatible interfaces, optimizing web performance, and integrating REST APIs into dynamic frontend applications. Hands-on teaching experience with web technologies at NxtWave, reinforcing deep foundational knowledge in HTML, CSS, JavaScript, and React component architecture.

%----------TECHNICAL SKILLS----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Frontend}{: React, Angular, Vite, Redux, Context API, HTML5, CSS3, Tailwind CSS, Responsive Design, Cross-Browser Compatibility} \\
    \textbf{JavaScript}{: ES6+, TypeScript, Async/Await, DOM Manipulation, Event Handling, Component Architecture} \\
    \textbf{Backend}{: Node.js, Express.js, Flask, FastAPI, RESTful APIs, JWT Authentication, MVC Pattern} \\
    \textbf{Databases}{: MongoDB, PostgreSQL, MySQL, SQLite, Database Schema Design, Query Optimization} \\
    \textbf{Web Performance}{: Code Splitting, Lazy Loading, API Optimization, sub-150ms Response Times} \\
    \textbf{Tools \& DevOps}{: Git, GitHub, Docker, AWS, Linux, CI/CD, Postman, Figma} \\
    \textbf{Languages}{: JavaScript, TypeScript, Python, Java, C++, SQL, Bash} \\
    \textbf{Core CS}{: Data Structures, OOP, System Design, Agile/Scrum, DBMS}
  }}
\end{itemize}
\vspace{-16pt}

%----------EDUCATION----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{VIT-AP University, Amaravathi}{Nov 2021 -- Present}
{Integrated M-Tech in Software Engineering (Computer Science)}{CGPA: 8.33/10}
\resumeSubheading
{Narayana Junior College, Vizag}{May 2018 -- July 2020}
{Intermediate (MPC)}{CGPA: 8.88/10}
\resumeSubHeadingListEnd

%----------WORK EXPERIENCE----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Development Instructor Intern}{Apr 2026 -- Present}
{NxtWave Disruptive Technologies}{Hyderabad, IN (Hybrid)}
\resumeItemListStart
\resumeItem{Taught frontend web development to students covering HTML5, CSS3, JavaScript (ES6+), and React — reinforcing deep expertise in responsive layouts, component-based architecture, and UI best practices.}
\resumeItem{Reviewed and debugged student web projects daily, guiding fixes around cross-browser compatibility, layout issues, API integration, and JavaScript performance bottlenecks.}
\resumeItem{Created and refined instructional content including code walkthroughs, UI pattern breakdowns, and project-based challenges, improving learner engagement and practical skill retention.}
\resumeItemListEnd

\resumeSubheading
{Software \& Data Engineering Intern}{Jul 2024}
{Rashtriya Ispat Nigam Limited (Vizag Steel Plant)}{Visakhapatnam, IN}
\resumeItemListStart
\resumeItem{Developed a full-stack web application using React and Node.js for healthcare management, handling 5,000+ daily transactions with a responsive UI and reducing patient wait times by 20\%.}
\resumeItem{Built and integrated RESTful APIs connecting React frontend to PostgreSQL and MySQL backends, ensuring seamless data flow and consistent cross-device user experience.}
\resumeItem{Optimized SQL query performance through indexing and execution plan analysis, improving backend response times by 72\% — directly improving web application load performance.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}

%----------PROJECTS----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{CodeToCareer - Web Platform} $|$ \emph{React, Node.js, Express.js, MongoDB, Tailwind CSS, JWT}}{Dec 2025}
\resumeItemListStart
\resumeItem{Designed and developed a fully responsive web platform with React featuring course management, real-time discussion forums, and role-based dashboards serving 200+ active users.}
\resumeItem{Built a performant frontend with Tailwind CSS and React Router, achieving consistent rendering across Chrome, Firefox, and Safari with sub-150ms API response times for 95\% of endpoints.}
\resumeItem{Integrated JWT authentication flows, protected routing, and stateful session management across the frontend and Express.js backend.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{AI Interview Preparation Bot} $|$ \emph{React, Node.js, Azure OpenAI, MongoDB, REST API}}{Jan 2026}
\resumeItemListStart
\resumeItem{Built a React-based SPA with dynamic form inputs, file upload (PDF resume parsing), and real-time AI-generated Q\&A rendering — delivering a smooth, interactive web experience.}
\resumeItem{Designed and consumed a custom REST API layer integrating Azure OpenAI, reducing interview preparation time by 40\% through responsive, context-aware UI feedback loops.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Smart Attendance System} $|$ \emph{Python, OpenCV, CNN, MySQL, Web Dashboard}}{Aug 2024}
\resumeItemListStart
\resumeItem{Developed an automated facial recognition attendance system with a web-accessible reporting dashboard, enabling real-time data querying across 300+ daily entries for 500+ student profiles.}
\resumeItem{Achieved 98\% detection accuracy and reduced manual attendance processing by 90\% through seamless integration of Python backend processing with database-driven web reporting.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Spam Email Detection System} $|$ \emph{Python, Flask, REST API, Scikit-learn, NLP}}{Mar 2025}
\resumeItemListStart
\resumeItem{Built a Flask-powered web API serving an NLP classification model trained on 15,000+ samples, exposing a clean REST endpoint for real-time spam detection with 96\% precision.}
\resumeItem{Packaged the ML pipeline (tokenization, TF-IDF, inference) behind a web API interface, demonstrating ability to bridge data science outputs into deployable web services.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-15pt}

%----------CERTIFICATIONS----------
\section{Certifications \& Achievements}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{Gemini Certified University Student} $|$ \emph{Google}}{Dec 2025}
\resumeProjectHeading
{\textbf{Object Oriented Programming - Basics to Advanced} $|$ \emph{Udemy}}{Nov 2023}
\resumeProjectHeading
{\textbf{University Chess Player} $|$ \emph{Logical thinking and systematic problem solving}}{}
\resumeSubHeadingListEnd

\end{document}
